---
title: "Evaluating Models"
format:
  revealjs: 
    slide-number: true
    theme: [default, tidymodels.scss]
    width: 1280
    height: 720
knitr:
  opts_chunk: 
    echo: true
    collapse: true
    comment: "#>"
---

```{r}
#| include: false
#| file: setup.R
```

## Metrics for model performance

```{r}
#| echo: false
library(tidymodels)
library(countdown)
library(tidyverse)
data("tree_frogs", package = "stacks")
tree_frogs <- tree_frogs %>%
  mutate(t_o_d = factor(t_o_d),
         age = age / 86400) %>% 
  filter(!is.na(latency)) %>%
  select(-c(clutch, hatched))

set.seed(123)
frog_split <- initial_split(tree_frogs, prop = 0.8, strata = latency)
frog_train <- training(frog_split)
frog_test <- testing(frog_split)
tree_spec <- decision_tree(cost_complexity = 0.001, mode = "regression")
tree_wflow <- workflow(latency ~ ., tree_spec)
tree_fit <- fit(tree_wflow, frog_train)
```

```{r}
augment(tree_fit, new_data = frog_test) %>%
  metrics(latency, .pred)
```

. . .

-   RMSE: difference between the predicted and observed values ⬇️
-   $R^2$: squared correlation between the predicted and observed values ⬆️
-   MAE: similar to RMSE, but mean absolute error ⬇️

## Metrics for model performance

```{r}
augment(tree_fit, new_data = frog_test) %>%
  rmse(latency, .pred)
```

## Metrics for model performance

```{r}
augment(tree_fit, new_data = frog_test) %>%
  group_by(reflex) %>%
  rmse(latency, .pred)
```

# ⚠️ DANGERS OF OVERFITTING ⚠️

## Dangers of overfitting ⚠️

```{r overfitting1}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/tuning-overfitting-train-1.svg")
```

## Dangers of overfitting ⚠️

```{r overfitting2}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/tuning-overfitting-test-1.svg")
```

We call this "resubstitution" or "repredicting the training set"

. . .

What if we want to compare more models?

. . .

And/or more model configurations?

. . .

And we want to understand if these are important differences?

# The testing data are precious 💎

# How can we use the *training* data to compare and evaluate different models? 🤔

## Resampling
```{r resampling1}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/resampling.svg")
```

## Cross-validation

```{r cv1}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/three-CV.svg")
```


## Cross-validation

```{r cv2}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/three-CV-iter.svg")
```

# Alternate resampling schemes

## Bootstrapping

```{r boot1}
#| echo: false
#| out-width: '70%'
#| fig-align: 'center'
knitr::include_graphics("images/bootstraps.svg")
```
